2010 Progress Report to Joshua Toolkit : An Open Source Toolkit for Parsing-based Machine Translation\thanks{ Please cite Li et al. (2009a) if you use Joshua in your research, and not this paper.}

### 2010-04-23 papers/wmt10/joshua-progress.tex
more stuff
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1604 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\title{Joshua: An Open Source Toolkit for Parsing-based Machine Translation\thanks{ 
Please cite Li et al. (2009a) if you use Joshua in your research, and not this paper. }}

\author{
Zhifei Li,\,\,\,
Chris Callison-Burch,\,\,\,
Chris Dyer,$^\dagger$\,\,\,
Juri Ganitkevitch,\,\,\,
Ann Irvine,\,\,\, 
Sanjeev Khudanpur,\,\,\,\\ {\bf
Lane Schwartz,$^\star$\,\,\, 
Wren N.\,G.\,Thornton,\,\,\,
Ziyuan Wang,\,\,
Jonathan Weese\,\,
{\textnormal{and}}
\,\,\,Omar F. Zaidan}\\
Center for Language and Speech Processing, Johns Hopkins University, Baltimore, MD\\
$\dagger$ Computational Linguistics and Information Processing Lab, University of Maryland, College Park, MD\\
$\star$ Natural Language Processing Lab, University of Minnesota, Minneapolis, MN }

@@

\begin{document}
\maketitle

\begin{abstract}
 This paper describes Joshua 2.0, an open source hierarchical phrase-based statistical machine translation system.
\end{abstract}

@@

@@

@@

@@

@@

\section{Manual Constraints}
\todo{anni}

%\todo{Add info about grammar extraction; MT Marathon paper and speedups}
%
%\section{Results}
%
%\todo{Describe results}
%
%\begin{table}[h]
%\begin{center}
%\begin{tabular}{|l|l||c|c|c|}
%\hline
%\bf Source & \bf Target & \bf BLEU & \bf BLEU- & \bf TER \\
%& & & \bf cased & \\
%\hline
%German & English & 21.3 & 19.5 & 0.660 \\ \hline
%English & German & 15.2  & 14.6  & 0.738 \\ \hline
%French & English & 27.7 & 26.4 & 0.614 \\ \hline
%English & French & 23.8 & 22.8 & 0.681 \\ \hline
%Spanish & English & 29.0 & 27.6 & 0.595 \\ \hline
%English & Spanish & 28.1 & 26.5 & 0.596  \\ \hline
%\end{tabular}
%\end{center}
%\caption{\label{scores} Automatic metric scores for the test set newstest2010 }
%\end{table}
%
%
%\begin{table}[h]
%\begin{center}
%\begin{tabular}{|l|l||c|}
%\hline
%\bf Source & \bf Target & \bf BLEU  \\
%\hline
%German & English & 18.19  \\ \hline
%English & German & 13.57 \\ \hline
%French & English & 26.41 \\ \hline
%English & French & 25.28 \\ \hline
%Spanish & English & 25.28 \\ \hline
%English & Spanish & 24.02  \\ \hline
%\end{tabular}
%\end{center}
%\caption{\label{devtest-scores} Automatic metric scores for the development test set newstest2009}
%\end{table}

>>>>

\newcommand{\joshua}{\textbf{Joshua}}

\title{2010 Progress Report to Joshua Toolkit : An Open Source Toolkit for Parsing-based Machine Translation\thanks{ 
Please cite Li et al. (2009a) if you use Joshua in your research, and not this paper.}}

\author{
Zhifei Li,\,\,\,
Chris Callison-Burch,\,\,\,
%Chris Dyer,$^\dagger$\,\,\,
Juri Ganitkevitch,\,\,\,
Ann Irvine,\,\,\, 
%Sanjeev Khudanpur,\,\,\,
Lane Schwartz,$^\star$\,\,\, 
\\ {\bf
Wren N.\,G.\,Thornton,\,\,\,
Ziyuan Wang,\,\,
Jonathan Weese\,\,
{\textnormal{and}}
\,\,\,Omar F. Zaidan}\\
Center for Language and Speech Processing, Johns Hopkins University, Baltimore, MD\\
%$\dagger$ Computational Linguistics and Information Processing Lab, University of Maryland, College Park, MD\\
$\star$ Natural Language Processing Lab, University of Minnesota, Minneapolis, MN }

@@

\begin{document}

\maketitle
\begin{abstract}
We describe the progress we have made in the past year to \textbf{Joshua} \cite{joshua-wmt09}, 
an open-source toolkit for parsing-based machine translation.
The main new functions we have added into the toolkit include: supporting for the syntax-augmented machine translation (SAMT) grammar,
supporting mannual constraints in the input to constrain the decoding,  
semiring parsing for unified dynamic programming, hypergraph-based 
discriminative training for better feature engineering, visualization of the derivation
trees and hypergraphs, and a unified pipeline for MT experiments.
\end{abstract}

@@

\section{Introduction}

\textbf{Joshua} \cite{joshua-wmt09} is an open-source toolkit (written in Java) for parsing-based machine translation.
In the first version, it  has inimplemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
It has also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007} 
and minimum error rate training \cite{och-mert}. 
Additionally, parallel and distributed computing techniques have been exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

The toolkit has then been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this report, we will describe the main new functions we have added into the 
toolkit, which include: supporting for the syntax-augmented machine translation (SAMT) grammar \cite{???},
supporting mannual constraints in the input to constrain the decoding \cite{???},  
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP}, 
hypergraph-based discriminative training for better feature engineering \cite{oracle-extraction-naacl09}, 
visualization of the derivation trees and hypergraphs \cite{???}, 
and a unified pipeline for MT experiments \cite{???}.

Below we give a short description for each of the new functions added.

@@

\section{Supporting Manual Constraints}
\todo{anni}

@@

\cite{li-eisner:2009:EMNLP}

@@

\cite{variational-decoding-acl09}
\cite{oracle-extraction-naacl09}

@@

\section{MT Pipeline}
\todo{lane}

\bibliographystyle{acl}
\bibliography{machinetranslation}
